Response Letter for manuscript TSUSC-2018-12-0140 \\ ``Online EV Scheduling Algorithms for Adaptive Charging Networks with Global Peak Constraints'' \\ \vspace{4mm} \large by Bahram~Alinia, Mohammad~H.~Hajiesmaili, Zachary J. Lee, Noel Crespi, and Enrique Mallada

### 2019-08-28 TSC/R1/TSC.tex
Finalizing main and response file for submission

\subsubsection{Worst-case Analysis in Similar Scheduling Problems}
\label{sec:rel:comp}
\bt{
	Similar underlying scheduling problems with slightly different settings have been studied in the literature in both offline and online settings. In offline setting, the problem is more interesting in integral revenue model where the problem becomes a combinatorial optimization problem and approximation algorithms have been used to find effective solutions. 
The performance of an approximation algorithm is determined by its \emph{approximation ratio} for offline 
algorithms. On the other hand, competitive online algorithms are used in the online setting and \emph{competitive ratio} is the performance metric which compares the algorithm's result to the offline optimal solution.

@@

		\subsection{Problem Formulation}
		\label{sec:problem}
	We formulate an optimization problem to schedule the charging of the EVs with the objective of maximizing total revenue obtained from charged EVs while respecting local and global peak constraints. 
		Note that each revenue model makes the underlying optimization problem fundamentally different. More specifically, the fractional charging model is a linear problem. 
		Integral revenue model, however, turns the underlying charging scheduling problem to a Mixed Integer Linear Program (MILP). The integer nature originates from the $0/1$-selection decision on EVs. 
%%%Recall that in integral revenue model the revenue is obtained given that the entire demand is fulfilled for the selected EV. 
		%We skip the explicit formulation of the problem under integral revenue model since it could be contemplated as the linear-relaxed version of the integral revenue model (for more explanation, we refer to the discussions in Section~\ref{sec:fractional}).
		We formulate Scheduling Problem for Adaptive charging Network (\MCSP) under fractional revenue model as follows: 
		\bse
		\bee
		\MCSP: \max  && \sum\nolimits_{i=1}^n \frac{v_{i}}{D_i}\sum\nolimits_{t=a_i}^{d_i} y_i^t \label{Pobjec} \nonumber\\
		\text{s.t.} &&\sum\nolimits_{t=a_i}^{d_i} y_i^t\leq D_i,\quad\quad\forall i, \label{ConstPartial} \\
		&&  \sum\nolimits_{i=1}^n y_i^t\leq p^\mathsf{total} ,\quad\quad\forall t,\label{ConstTotal} \\
		&&\sum\nolimits_{i:h(i)=j} y_i^t\leq p_j ,\quad\quad\forall t,j,\label{ConstLocal}\\
		&& y_i^t  \leq \frac{k_i}{D_i}\sum\nolimits_{t^\prime=a_i}^{d_i} y_i^{t^\prime}, \quad\forall i,t,\label{ConstSpeed}\\
%		&& \rev{y_i^t=0,\forall t\in\{t':t'>d_i \vee t'<a_i\}}, \\
		\text{vars.} && y_i^t \geq 0, \quad\quad\forall i, t,\label{ConstPositive}\nonumber
		%&& s_v(t), \quad \forall v,t
		\eee
		\ese
		where $y_i^t$ is the amount that EV $i$ is charged at slot $t$. Constraint (\ref{ConstPartial}) ensures that the aggregate amount received by EV $i$ is at most the demand $D_i$. 
%		Note that under integral revenue model, when we design our algorithm, we do not allow partial charging. 
The global and local peak constraints are represented by constraints (\ref{ConstTotal}) and (\ref{ConstLocal}), respectively.

@@

\revv{
\subsection{Optimal Offline Design}
\label{sec:fopt}	
\bt{
In this section, we propose an optimal algorithm for offline fractional model. As a natural solution, one may think of a greedy algorithm with the strategy as follows: at each time slot, charge the EV with highest unit-value and process others if only the resource cannot be used by this EV (probably due to maximum charging rate constraint). 
This approach is a popular, yet straightforward method in the online scheduling. However, it turns out that this approach cannot provide an optimal solution to the problem even in fractional revenue model. In fact, this approach only provides a 2-competitive solution. i.e., the profit obtained by the algorithm would be $1/2$ of the optimum. As an intuition of the proof think of two EVs where the one with lower unit value cannot wait due to its deadline and the EV with higher unit value has a long park time. Then, the optimal solution here could be first serving the EV with earlier deadline (and not the one with highest unit values).
}

@@

		\subsubsection{Analysis}
		\label{subsec:analysis}
		In primal-dual algorithm, the goal is to design an algorithm in a way that it produces a good solution for primal problem (with primal value $\Gamma$) and a feasible solution for the dual problem (with dual value $\Lambda$). Then, assuming that the primal problem is a maximization problem, to prove that the algorithm is $c-$approximation (for $c\geq 1$), the important part is to show that $\Lambda\leq c\Gamma$. Then, based on weak duality theorem we have $\Lambda\geq \opt$, and it is concluded that $\Gamma \geq \frac{1}{c}\times\opt$ where $\opt$ is the optimal value. 
		Based on the above understanding, the following theorem scrutinizes the approximation ratio of the \ics assuming that arrival times are the same for all EVs. 
%		First note that the designed scheduling algorithm outputs a feasible scheduling since it respects the constraints in the primal problem. Also, the algorithm produces a feasible solution for the dual problem by covering the dual problem constraint in (\ref{ConstDcover}) through setting $\alpha _i$ to $\frac{v_i}{D_i}$ when EV $i$ is accepted and, $\beta (t)$ to a value greater than or equal to $\frac{v_i}{D_i}$ for $t\in [a_i, d_i]$ (according to the discussion in Section \ref{sec:icsexplanation}) if EV $i$ is not selected. To obtain an approximation factor for the algorithm, it is enough to bound the total covering cost of the dual constraints.

@@

\subsection{Online Scenario}
\label{sec:onlineint}
Due to the binary selection variable, the online solution design under integral model is more challenging than the one for fractional model. We propose the \iocs that is built upon the offline \ics. In particular, the \iocs calls the \ics at each time slot for the set of available EVs, however, any algorithm that is designed for offline integral model can be used alternatively. Hereinafter, $\mathcal{A}$ refers to the \ics or a similar algorithm.

@@

The \iocs is summarized as Algorithm~\ref{alg:iocs}. At slot $t$, the \iocs compares two scheduling results returned by $\mathcal{A}$ and chooses among them. In the first scheduling, the \iocs keeps all reserved resources in interval $[t,T]$ intact. Then, for utilizing the remaining resources, the algorithm runs $\mathcal{A}$ over arrived EVs at time slot $t$. In this case, the total revenue obtained by the \emph{active} EVs (i.e., EVs that are available but not received their entire demand yet) is denoted by $\widehat{\Gamma}_{\mathcal{A},\mathcal{R}^t}$ (Line $6$ of the algorithm). In the second scheduling, the \iocs considers the case that it can sacrifice the previously admitted EVs by canceling their reservations and allocating the freed resources to more valuable demands. For this purpose, the algorithm modifies the demand and valuation of the previously admitted EVs such that each demand is replaced by the EV's remaining demand, and the valuation of the EV is proportionally calculated based on the remaining demand (Line $9$ of the algorithm) so that the unit values of EVs do not change. Then, the \iocs runs $\mathcal{A}$ over set of active EVs $\mathcal{M}^t$ where the corresponding gain is denoted by $\Gamma_{\mathcal{A},\mathcal{M}^t}$. If $\Gamma_{\mathcal{A},\mathcal{M}^t}>\widehat{\Gamma}_{\mathcal{A},\mathcal{R}^t}$, the \iocs forgets the previously admitted EVs and follows the second scheduling.

@@

The following theorem characterizes the competitive ratio of the \iocs in a special case. 
\begin{thm}
\label{thm:iocscompetitive}
Let $\mathcal{A}$ be \ics in \iocs algorithm and $m=1$. Assuming that EVs are released in $b$ distinct groups where arrival time of EVs in each group are the same, the \iocs is $b\Big(1+\frac{p}{p-q}\frac{s}{s-1}\Big)$-competitive with optimal offline solution, where $p$ is the station peak and $q=\max_i k_i, i=1,\dots ,n$. 
\end{thm}

@@

				\caption{\revv{Comparison results for $2$, $4$, and $8$ CSs for fractional and integral revenue models.}} 

@@

The peak intervals include $08$:$00$-$10$:$00$, $12$:$00$-$14$:$00$, and $18$:$00$-$20$:$00$ which is in accordance to NHTS survey~\cite{Santos, Tang}. \revv{The probability of arriving an EV in the peak hours is two times higher than the off-peak periods.

@@

The proposed algorithms compared to the optimal offline solution of integral model ($\textsc{iOPT}$) and $\iolp$. \bt{Note that comparison with offline optimal could be considered as a baseline comparison with the category of approximate offline algorithms in integral model~\cite{yao2016real}.}

@@

%\input{intro.tex}
%\input{rel.tex}
%\input{sys.tex}		
%\input{fraction.sol.tex}		
%\input{integral.sol.tex}
%\input{exp.tex}
%%%\vspace{0.1mm}
%\input{conc.tex}
%\newpage
%ss
%\newpage
%\pagestyle{empty}
\bibliography{ref}{}
%\vspace{-2.8mm}
\bibliographystyle{ieeetr}

>>>>

\subsubsection{Worst-case Analysis in Similar Scheduling Problems}
\label{sec:rel:comp}
\bt{
	Similar underlying scheduling problems with slightly different settings have been studied in the literature in both offline and online settings. In offline setting, the problem is more interesting \bt{under integral revenue model} where the problem becomes a combinatorial optimization problem and approximation algorithms have been used to find effective solutions. 
The performance of an approximation algorithm is determined by its \emph{approximation ratio} for offline 
algorithms. On the other hand, competitive online algorithms are used in the online setting and \emph{competitive ratio} is the performance metric which compares the algorithm's result to the offline optimal solution.

@@

		\subsection{Problem Formulation}
		\label{sec:problem}
	We formulate an optimization problem to schedule the charging of the EVs with the objective of maximizing total revenue obtained from charged EVs while respecting local and global peak constraints. 
		Note that each revenue model makes the underlying optimization problem fundamentally different. More specifically, the fractional charging model is a linear problem. 
		Integral revenue model, however, turns the underlying charging scheduling problem to a Mixed Integer Linear Program (MILP). The integer nature originates from the $0/1$-selection decision on EVs. 
%%%Recall that in integral revenue model the revenue is obtained given that the entire demand is fulfilled for the selected EV. 
		%We skip the explicit formulation of the problem under integral revenue model since it could be contemplated as the linear-relaxed version of the integral revenue model (for more explanation, we refer to the discussions in Section~\ref{sec:fractional}).
		\bt{We formulate a Scheduling Problem} for Adaptive charging Network (\MCSP) under fractional revenue model as follows: 
		\bse
		\bee
		\MCSP: \max  && \sum\nolimits_{i=1}^n \frac{v_{i}}{D_i}\sum\nolimits_{t=a_i}^{d_i} y_i^t \label{Pobjec} \nonumber\\
		\text{s.t.} &&\sum\nolimits_{t=a_i}^{d_i} y_i^t\leq D_i,\quad\quad\forall i, \label{ConstPartial} \\
		&&  \sum\nolimits_{i=1}^n y_i^t\leq p^\mathsf{total} ,\quad\quad\forall t,\label{ConstTotal} \\
		&&\sum\nolimits_{i:h(i)=j} y_i^t\leq p_j ,\quad\quad\forall t,j,\label{ConstLocal}\\
		&& y_i^t  \leq \frac{k_i}{D_i}\sum\nolimits_{t^\prime=a_i}^{d_i} y_i^{t^\prime}, \quad\forall i,t,\label{ConstSpeed}\\
%		&& \rev{y_i^t=0,\forall t\in\{t':t'>d_i \vee t'<a_i\}}, \\
		\text{vars.} && y_i^t \geq 0, \quad\quad\forall i, t,\label{ConstPositive}\nonumber
		%&& s_v(t), \quad \forall v,t
		\eee
		\ese
		where $y_i^t$ is the amount that EV $i$ is charged at slot $t$. Constraint (\ref{ConstPartial}) ensures that the aggregate amount received by EV $i$ is at most the demand $D_i$. 
%		Note that under integral revenue model, when we design our algorithm, we do not allow partial charging. 
The global and local peak constraints are represented by constraints (\ref{ConstTotal}) and (\ref{ConstLocal}), respectively.

@@

\revv{
\subsection{Optimal Offline Design}
\label{sec:fopt}	
\bt{
In this section, we propose an optimal algorithm for offline fractional model. As a natural solution, one may think of a greedy algorithm as follows: at each time slot, charge the EV(s) with highest unit-value and process others if only the remaining resource cannot be allocated to the selected EV(s) (e.g., due to maximum charging rate constraint or fulfillment of the EVs' demand). 
This approach is a popular, yet straightforward method in the scheduling. However, it turns out that this approach cannot provide an optimal solution to the problem even in fractional revenue model. In fact, this solution is only 2-approximation (i.e., the profit obtained by the algorithm would be $1/2$ of the optimum). As an intuition of the proof think of two EVs in a single charging station with power capacity $p$ and $\frac{v_1}{D_1}-\frac{v_2}{D_2}=\epsilon$  where $\epsilon > 0$ is an arbitrary small number, $a_1=a_2=1, d_1=2, d_2=1$ and $D_1=D_2=k_1=k_2=p$. Then, applying the simple greedy, EV 1 will be selected at time slot 1 and EV 2 will have no chance to get charged due to its deadline constraint while EV 1 could wait until time slot 2 and still receive all its demand.
}

@@

		\subsubsection{Analysis}
		\label{subsec:analysis}
		\bt{In a primal-dual algorithm}, the goal is to design an algorithm in a way that it produces a good solution for primal problem (with primal value $\Gamma$) and a feasible solution for the dual problem (with dual value $\Lambda$). Then, assuming that the primal problem is a maximization problem, to prove that the algorithm is $c-$approximation (for $c\geq 1$), the important part is to show that $\Lambda\leq c\Gamma$. Then, based on weak duality theorem we have $\Lambda\geq \opt$, and it is concluded that $\Gamma \geq \frac{1}{c}\times\opt$ where $\opt$ is the optimal value. 
		Based on the above understanding, the following theorem scrutinizes the approximation ratio of the \ics assuming that arrival times are the same for all EVs. 
%		First note that the designed scheduling algorithm outputs a feasible scheduling since it respects the constraints in the primal problem. Also, the algorithm produces a feasible solution for the dual problem by covering the dual problem constraint in (\ref{ConstDcover}) through setting $\alpha _i$ to $\frac{v_i}{D_i}$ when EV $i$ is accepted and, $\beta (t)$ to a value greater than or equal to $\frac{v_i}{D_i}$ for $t\in [a_i, d_i]$ (according to the discussion in Section \ref{sec:icsexplanation}) if EV $i$ is not selected. To obtain an approximation factor for the algorithm, it is enough to bound the total covering cost of the dual constraints.

@@

\subsection{Online Scenario}
\label{sec:onlineint}
Due to the binary selection variable, the online solution design under integral model is more challenging than the one for fractional model. \bt{We propose \iocs} that is built upon the offline \ics. In particular, the \iocs calls the \ics at each time slot for the set of available EVs, however, any algorithm that is designed for offline integral model can be used alternatively. Hereinafter, $\mathcal{A}$ refers to the \ics or a similar algorithm.

@@

The \iocs is summarized as Algorithm~\ref{alg:iocs}. At slot $t$, the \iocs compares two scheduling results returned by $\mathcal{A}$ and chooses among them. In the first scheduling, the \iocs keeps all reserved resources in interval $[t,T]$ intact. Then, for utilizing the remaining resources, the algorithm runs $\mathcal{A}$ over arrived EVs at time slot $t$. In this case, the total revenue obtained by the \emph{active} EVs (i.e., EVs that are available but not received their entire demand yet) is denoted by $\widehat{\Gamma}_{\mathcal{A},\mathcal{R}^t}$ (Line $6$ of the algorithm). In the second scheduling, the \iocs considers the case that it can sacrifice the previously admitted EVs by canceling their reservations and allocating the freed resources to more valuable demands. For this purpose, the algorithm modifies the demand and valuation of the previously admitted EVs such that each demand is replaced by the EV's remaining demand, and the valuation of the EV is proportionally calculated based on the remaining demand (Line $9$ of the algorithm) so that the unit values of EVs do not change. Then, the \iocs runs $\mathcal{A}$ \bt{on set of} active EVs $\mathcal{M}^t$ where the corresponding gain is denoted by $\Gamma_{\mathcal{A},\mathcal{M}^t}$. If $\Gamma_{\mathcal{A},\mathcal{M}^t}>\widehat{\Gamma}_{\mathcal{A},\mathcal{R}^t}$, the \iocs forgets the previously admitted EVs and follows the second scheduling.

@@

The following theorem characterizes the competitive ratio of the \iocs in a special case. 
\begin{thm}
\label{thm:iocscompetitive}
Let $\mathcal{A}$ be \ics in \iocs algorithm and $m=1$. Assuming that EVs are released in $b$ distinct groups where arrival time of EVs in each group are the same, the \iocs is $b\Big(1+\frac{p}{p-q}\frac{s}{s-1}\Big)$-competitive \bt{with optimal} offline solution, where $p$ is the station peak and $q=\max_i k_i, i=1,\dots ,n$. 
\end{thm}

@@

				\caption{\revv{Comparison results for $2$, $4$, and $8$ CSs for fractional and integral revenue models. \bt{In the algorithms' name, letters ``o'', ``f'' and ``i'' indicate online, fractional and integral, respectively. Note that a ``non-optimal'' fractional algorithm can potentially achieve better result than an ``optimal'' integral algorithm due to higher flexibility in power allocation.} }} 

@@

The peak intervals include $08$:$00$-$10$:$00$, $12$:$00$-$14$:$00$, and $18$:$00$-$20$:$00$ \bt{according to NHTS} survey~\cite{Santos, Tang}. \revv{The probability \bt{of an EV's arrival} during the peak hours is two times higher than the off-peak periods.

@@

\bt{The proposed algorithms are compared to} the optimal offline solution of integral model ($\textsc{iOPT}$) and $\iolp$. \bt{Note that comparison with offline optimal could be considered as a baseline comparison with the category of approximate offline algorithms in integral model~\cite{yao2016real}.}

@@

%\input{intro.tex}
%\input{rel.tex}
%\input{sys.tex}		
%\input{fraction.sol.tex}		
%\input{integral.sol.tex}
%\input{exp.tex}
%%%\vspace{0.1mm}
%\input{conc.tex}
%\newpage
%ss
%\newpage
%\pagestyle{empty}
\bibliography{ref}{}
%\vspace{-2.8mm}
\bibliographystyle{ieeetr}
\newpage
{\color{white}...}    
\newpage

### 2019-08-28 TSC/R1/res.tex
Finalizing main and response file for submission

\ifodd 1
\newcommand{\bt}[1]{{\color{red}#1}}%revise of the text
\newcommand{\rev}[1]{{\color{black}#1}}%revise of the text
\newcommand{\com}[1]{\textbf{\color{red}(Bahram says: #1)}}%comment of the text
\newcommand{\comm}[1]{\textbf{\color{red}(Mohammad says: #1)}}%comment of the text
\else
\newcommand{\bt}[1]{#1}
\newcommand{\rev}[1]{#1}
\newcommand{\com}[1]{}
\fi

@@

We are very grateful for handling our paper and the time and effort that you and your team put into the process. We have thoroughly revised our manuscript based on your and the referees' constructive comments. This document provides a summary of changes made in the revised manuscript and detailed responses to the comments of the reviewers. The major changes in the revised manuscript are summarized below:

\begin{enumerate}
\item \textit{\color{red} @Mohammad: better to remove this bullet section as we don't have many items to talk about (the only main change is in Related Work)}.

\end{enumerate}

@@

In addition, in the paper, we clearly distinguished between the results in this paper and our previous conference paper on IEEE/ACM IWQoS 2018. Our work in this paper considers more general problem formulation, with global peak constraints, multiple station scenario and a comprehensive revenue model. \bt{Although  ``fractional revenue'' model is studied in both papers (and in some other studies), the proposed algorithms are  different in idea, results and underlying system model. Also, the Section V for the integral revenue model is new in this work. Finally, the trace-driven experimental results are more extensive in this paper and provide comparisons with an algorithm that are currently in use in a real-world charging station. }

@@

$\vartriangleright$ \noindent\textbf{Response:} 
Our earlier work presents algorithms for only fractional revenue model. Current manuscript, which can be considered as journal extension of the previous work, studies both fractional and integral models. Although the presented algorithms in the conference version provide a competitive ratio of $2-1/U$ (with $U$ as "scarcity level"), the proof holds when all EVs have the same maximum charging rate. In the current study, we consider heterogeneity in this parameter and prove the online algorithm is 2-competitive.

\bt{To clarify this, we added an explanation in last paragraph of the Introduction section and Section II-3 when describing related works.   }

@@

{\color{red}: @Mohammad: This is not clear for me in most parts}

@@

$\vartriangleright$ \noindent\textbf{Response:} 
The current experiments (i) shows the effect of problem parameters, including the number of charging stations and number of vehicles (in Figure 2), and the impact of peak constraint and demand (in directly) (in Figure 3). The impact of arrival and departure times could be interpreted as more/less flexibility in charging scheduling. Our result in Figure 3, indeed, investigates the impact of flexibility in charging scheduling.

@@

$\vartriangleright$ \noindent\textbf{Response:} 
We listed pseudo-codes for all proposed algorithms (Algorithm 1-7) in the main body of the paper. Despite the technical challenges in the analysis, the main body of the algorithms are fairly simple and an interested reader can easily convert them to real implementation code. Last, we have provided some sample code implementations of our algorithms in 
%We believe that detailed implementation of the algorithms has no added value as the goal here is to provide algorithms and analysis and not focusing on programming challenges.
here: https://github.com/bahramalinia/EV-Scheduling.git

@@

$\vartriangleright$ \noindent\textbf{Response:} 
Thanks for the point. We agree that our problem is strongly NP-Hard and we corrected the related phrases in the manuscript. Please see Page ?? of the revised manuscript.

@@

$\vartriangleright$ \noindent\textbf{Response:} 
The constraint (1d) applies on each time slot $t$ for each EV $i$ and enforces respecting maximum charging rate at each $t$ for all $i$. The constraint say nothing about the relation between charging rates at different slots (including forcing them to be equal).

@@

$\vartriangleright$ \noindent\textbf{Response:} 
Thanks for the comment. This approach is equal to running an optimal algorithm at each time slot considering only available EVs and assuming no more EVs will arrive. We added a paragraph in the beginning of Section IV.A to explain this.

{\color{red}@ Mohammad: Should we use the following example in here or in the paper?}

We added an example in Page xx to demonstrate why the simple approach mentioned by the reviewer is not optimal.

The proposed approach by the reviewer is a popular, yet straightforward method in the online scheduling. However, it turns out that this approach cannot provide an optimal solution to the problem even in fractional revenue model. In fact, this approach only provides a 2-competitive solution. i.e., the profit obtained by this approach would be $1/2$ of the optimum. We bring an example to clarify.

Fig. \ref{fig:1a} shows a simple scenario in a single charging station with $T=2$ and $p_1=p^{\text{total}}=1$. The charging profile of an EV $i$ is shown in the form of $\pi_i=(a_i,d_i,v_i,D_i,k_i)$ where it is assumed that $k_i=1$ for all $i$.
At $t=1$, EVs 1 and 2 arrive and the scheduler has no information about the future coming EVs. If we run an optimal offline algorithm over the available EVs at $t=1$, it will allocate EV 2 at $t=1$ and postpone charging of EV 1 to $t=2$ according to their deadline. Now assume that EV 3 arrives at $t=2$ which has the same demand and unit value as EV 1 (see Fig. \ref{fig:1b}). Then, by re-computing the optimal solution at $t=2$, the solution is to choose either EV 1 or EV 3 to charge due to capacity constraint. Therefore, the final solution obtained by this approach achieves a total revenue of $1+\epsilon$ by charging EVs 2 at $t=1$ and one of the EVs 1 or 3 at $t=2$. However, the optimal solution in this example is charging EV 1 at $t=1$ and EV 3 at $t=2$ and obtaining a gain equal to 2. This example shows that the competitive ratio of the proposed approach by the reviewer cannot be better than $2-\epsilon$ where $\epsilon$ can be arbitrarily small.

\begin{figure}
\centering     %%% not \center
		\subfloat[{EVs $1$ and $2$ arrive at $t=1$.}]{\label{fig:1a}\includegraphics[width=60mm]{Ex1a.pdf}}
		\hspace{8mm}
		\subfloat[{EV $3$ arrives at $t=2$.}]{\label{fig:1b}\includegraphics[width=60mm]{Ex1b.pdf}}
\caption{Worst case scenario when the scheduling algorithm is to re-run an optimal algorithm at each time slot considering only available EVs. Dotted line indicates a time slot that is not visited yet and the scheduler has no information about the arriving EVs in that slot. The numbers inside parentheses indicate arrival time, deadline, value, demand and maximum charging rate of the EV, respectively.}
\label{fig:1}
\end{figure}

@@

$\vartriangleright$ \noindent\textbf{Response:} 
We agree and this is unfortunately consequence of space limit. To avoid confusion, we added an explanation in Page xx, when describing the results.

@@

$\vartriangleright$ \noindent\textbf{Response:} 
...

@@

{\color{red} I should check these papers and add to Related Work if needed.}

@@

$\vartriangleright$ \noindent\textbf{Response:} 
Although this can be an interesting extension, in this version, we assumed that a user chooses only one CS to ask for its demand and may drive to another CS if its demand is not fulfilled. We admit that this suggestion is a very elegant extension from the perspective of theoretical problem formulation and algorithm design, and makes the scenario more challenging. In addition, this suggestion makes more sense in scenarios in which EVs are heterogeneous and a subset of chargers can satisfy a subset of EVs. We do believe that this is an very interesting scenario to consider, however, as mentioned by the reviewer, it increases the complexity of designing and analysis of the algorithms, and is beyond the scope of this submission.

@@

B. Alinia, M. H. Hajiesmaili, and N. Crespi, "Online EV Charging Scheduling with On-Arrival Commitment", \textit{IEEE Trans. on Int. Transportation Systems (ITS)}, 2019.

In the above cited paper, we propose "SCOMMIT" algorithm where its core allocation idea is based on users' unit-values except that it also provides on-arrival commitment. Since it is proved that SCOMMIT is truthful, we believe that among the proposed algorithms in current manuscript, the FOCS is truthful. In the above paper, also, we tackled another desirable property to commit EVs on their arrival on how much they can get charged during their available window.

The focus of this paper, in on more comprehensive online algorithm design for fractional and integral revenue models, and for our ITS paper, we focused on truthfulness and on-arrival commitment. It is worth noting that developing solutions that provide competitiveness against offline optimal versus those that provide truthfulness and on-arrival commitment, needs different algorithmic techniques and tools. As a notable result, an interesting theoretical observation in our ITS shows that there is no online algorithms that can simultaneously provide on-arrival commitment and bounded competitive ratio. See Section 6 and Theorem 5 of our ITS paper for more details.

@@

$\vartriangleright$ \noindent\textbf{Response:} 
The length of the time slot can be arbitrary set in the algorithms and we used 1 hour in experiments since the availability window of our traces was in one hour slots. With more fine grained data, it would be possible to run the algorithms in faster timescales, e.g., 5 minutes or so.

We note that the derived complexities of the algorithms in the paper include parameter $T$ as number of time slots in a day (please see Table II in the manuscript). In large scale scenarios, the effect of increasing $T$ would be negligible in performance of the algorithms as long as it $T/N$ is a constant ($n$ is number of EVs). Therefore, when $n$ grows large and $T$ is a constant, $T$ can be removed from the complexities in the Table II.

@@

$\vartriangleright$ \noindent\textbf{Response:} 
\bt{As explained in the previous comment, we derived the time complexity of all proposed algorithms (listed in Table II in the paper) which indicate their running time in large scale scenarios (i.e., when $n$ is large). If we assume that $T$ is a constant (which is a quite realistic assumption), the complexity of all algorithms simplifies to $O(n^2)$. Hence, we believe that a normal PC could be fast enough to run the algorithms.}

>>>>

\ifodd 1
\newcommand{\bt}[1]{{\color{black}#1}}%revise of the text
\newcommand{\rev}[1]{{\color{black}#1}}%revise of the text
\newcommand{\com}[1]{\textbf{\color{red}(Bahram says: #1)}}%comment of the text
\newcommand{\comm}[1]{\textbf{\color{red}(Mohammad says: #1)}}%comment of the text
\else
\newcommand{\bt}[1]{#1}
\newcommand{\rev}[1]{#1}
\newcommand{\com}[1]{}
\fi

@@

We are very grateful for handling our paper and the time and effort that you and your team put into the process. We have thoroughly revised our manuscript based on your and the referees' constructive comments. This document provides a summary of changes made in the revised manuscript and detailed responses to the comments of the reviewers.

@@

In addition, in the paper, we clearly distinguished between the results in this paper and our previous conference paper on IEEE/ACM IWQoS 2018. Our work in this paper considers more general problem formulation, with global peak constraints, multiple station scenario and a comprehensive revenue model. \bt{Although  ``fractional revenue'' model is studied in both papers (and in some other studies as well), the proposed algorithms are  different in idea, results and underlying system model. Also, Section V for the integral revenue model is new in this work. Finally, the trace-driven experimental results are more extensive in this paper and provide comparisons with an algorithm that are currently in use in a real-world charging station. }

@@

$\vartriangleright$ \noindent\textbf{Response:} 
Our earlier work presents algorithms for only fractional revenue model. Current manuscript, which can be considered as an extension of the previous work, studies both fractional and integral models. Although the presented algorithms in the conference version provide a competitive ratio of $2-\frac{1}{U}$ (where $U$ denotes "scarcity level"), the proofs hold when all EVs have the same maximum charging rate. In the current study, we consider heterogeneity in this parameter and prove the online algorithm is 2-competitive.

\bt{To clarify this, we added an explanation in last paragraph of Introduction section in Page 2 and Section II-3 in Page 3 when describing related works.   }

@@

@@

$\vartriangleright$ \noindent\textbf{Response:} 
The current experiments (i) shows the effect of problem parameters, including the number of charging stations and number of vehicles (in Figure 2), and the impact of peak constraint and demand indirectly (Figure 3). The impact of arrival and departure times could be interpreted as more/less flexibility in charging scheduling. Our result in Figure 3, indeed, investigates the impact of flexibility in charging scheduling.

@@

$\vartriangleright$ \noindent\textbf{Response:} 
We listed pseudo-codes for all proposed algorithms (Algorithm 1-7) in the main body of the paper. Despite the technical challenges in the analysis, the main body of the algorithms are fairly simple and an interested reader can easily convert them to real implementation code. Last, we have provided some sample code implementations of our algorithms in 
%We believe that detailed implementation of the algorithms has no added value as the goal here is to provide algorithms and analysis and not focusing on programming challenges.
here: https://github.com/bahramalinia/EV-Scheduling

@@

$\vartriangleright$ \noindent\textbf{Response:} 
Thanks for the point. We agree that our problem is strongly NP-Hard and we corrected the related phrases in the manuscript.

@@

$\vartriangleright$ \noindent\textbf{Response:} 
The constraint (1d) applies on each time slot $t$ for each EV $i$ and ensures respecting maximum charging rate at each $t$ for all $i$. The constraint say nothing about the relation between charging rates at different slots (including forcing them to be equal).

@@

$\vartriangleright$ \noindent\textbf{Response:} 
Thanks for the comment.  
The proposed approach by the reviewer is a popular, yet straightforward method in the scheduling problems. However, it turns out that this approach cannot provide an optimal solution to the problem even in fractional revenue model. In fact, this approach only provides a 2-approximation solution. i.e., the profit obtained by this approach would be $1/2$ of the optimum. We added a paragraph in the beginning of Section IV.A to explain this with an example.

@@

$\vartriangleright$ \noindent\textbf{Response:} 
We agree and to avoid confusion, we added an explanation in the caption of Fig. 2 in page 10.

@@

$\vartriangleright$ \noindent\textbf{Response:} 
Thanks for the subtle comments. We corrected them.

@@

@@

$\vartriangleright$ \noindent\textbf{Response:} 
Although this can be an interesting extension, in this version, we assumed that a user chooses only one CS to ask for its demand and may drive to another CS if its demand is not fulfilled. We admit that this suggestion is a very elegant extension from the perspective of theoretical problem formulation and algorithm design, and makes the scenario more challenging. In addition, this suggestion makes more sense in scenarios in which EVs are heterogeneous and a subset of chargers can satisfy a subset of EVs. We do believe that this is an interesting scenario to consider, however, as mentioned by the reviewer, it increases the complexity of designing and analysis of the algorithms, and is beyond the scope of this submission.

@@

\begin{itemize}
\item B. Alinia, M. H. Hajiesmaili, and N. Crespi, "Online EV charging scheduling with on-arrival commitment," \textit{IEEE Transaction on Intelligent Transportation Systems}, Jan. 2019.
\end{itemize}

In the above cited paper, we propose "SCOMMIT" algorithm where its core allocation idea is based on users' unit-values except that it also provides on-arrival commitment. Since it is proved that SCOMMIT is truthful, we believe that among the proposed algorithms in current manuscript, the FOCS is truthful. In the above paper, also, we tackled another desirable property to give commitment to the users at their arrival time about the minimum amount of resource they can get by their deadline.

The focus of this paper is to consider more comprehensive online algorithm design for fractional and integral revenue models, while in the ITS paper, we focused on truthfulness and on-arrival commitment. It is worth noting that developing solutions that provide competitiveness against offline optimal versus those that provide truthfulness and on-arrival commitment, needs different algorithmic techniques and tools. As a notable result, an interesting theoretical observation in our ITS paper shows that there is no online algorithms that can simultaneously provide on-arrival commitment and bound the competitive ratio. See Section 6 and Theorem 5 of our ITS paper for more details.

@@

$\vartriangleright$ \noindent\textbf{Response:} 
The length of the time slot can be arbitrary set in the algorithms. However, we used 1 hour in the experiments since the availability window in our traces was in one hour slots. With more fine grained data, it would be possible to run the algorithms in faster timescales, e.g., 5 minutes or so.

We note that the derived complexities of the algorithms in the paper include parameter $T$ as number of time slots in a day (please see Table II in the manuscript). In large scale scenarios, the effect of increasing $T$ would be negligible in performance of the algorithms as long as it $T$ is a constant.

@@

$\vartriangleright$ \noindent\textbf{Response:} 
\bt{As explained in the response to the previous comment, we derived the time complexity of all proposed algorithms (listed in Table II in the paper) which indicate their running time in large scale scenarios (i.e., when $n$ as number of EVs grows large). If we assume that $T$ is a constant (which is quite realistic assumption), the complexity of all algorithms simplifies to $O(n^2)$. Hence, we believe that a normal PC could be fast enough to run the algorithms.}
